### 2017-10-10 reorganize/papers/elliott-thesis/latex/thesis.tex
Make stuff build on lab computers.

%% \subsection{Calculating one/bothbound times of experimental dynein}
%% In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\

%% \newcommand\tbb{\left<t_{bb}\right>}
%% \newcommand\tob{\left<t_{ob}\right>}
%% \newcommand\tstep{\left<t_{step}\right>}
%% \newcommand\tproc{\left<t_{processivity}\right>}
%% \newcommand\kub{k_{ub}}
%% \newcommand\kb{k_{b}}
%% \newcommand\ko{k_{dis}}

%% \begin{itemize}
%% \item $\tbb$: Time in bothbound per step
%% \item $\tob$: Time in onebound per step
%% \item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
%% \item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
%% \item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
%% \item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
%% \item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
%% \item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
%% \item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
%% \end{itemize}

%% $\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:

%% \begin{align*}
%%   \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
%%   &= \frac{\tstep-\tbb}{\tstep\tbb}\\
%%   \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
%%   \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
%%   \tob &= \tstep-\tbb\\
%%   &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
%%   &= \frac{\tstep^2}{\tstep+\tproc}\\
%% \end{align*}

%% Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:

%% \begin{figure}[h]
%%   \centering
%%   \begin{tabular}{| c | c | c | c | c | c |}
%%     \hline
%%     Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
%%     134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
%%   \end{tabular}
%%   \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
%%   \label{table:time-parameter-table}
%% \end{figure}

>>>>

\subsection{Calculating one/bothbound times of experimental dynein}
In order to fit parameters, a goodness metric for a simulation is needed. Time spent in onebound and bothbound states are good metrics. These values are calculated here.\\

\newcommand\tbb{\left<t_{bb}\right>}
\newcommand\tob{\left<t_{ob}\right>}
\newcommand\tstep{\left<t_{step}\right>}
\newcommand\tproc{\left<t_{processivity}\right>}
\newcommand\kub{k_{ub}}
\newcommand\kb{k_{b}}
\newcommand\ko{k_{dis}}

\begin{itemize}
\item $\tbb$: Time in bothbound per step
\item $\tob$: Time in onebound per step
\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
\end{itemize}

$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:

\begin{align*}
  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  \tproc &= \frac{\tstep\tbb}{\tstep-\tbb}\\
  \tbb &= \frac{\tproc\tstep}{\tproc+\tstep}\\
  \tob &= \tstep-\tbb\\
  &= \tstep - \frac{\tstep\tproc}{\tstep+\tproc}\\
  &= \frac{\tstep^2}{\tstep+\tproc}\\
\end{align*}

Thus, by the above equations and using data from \cite{weihongpaper}, values for $\tbb$ and $\tob$ can be found:

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:time-parameter-table}
\end{figure}
